Tabular Constraint Learning

### 2016-04-14 Paper/ECAI/tabular.tex
adding comments

\paragraph{Example}
Consider Table~1 in the Figure~\ref{fig:main_example}, its rows are not type consistent (i.e. they contain both numeric and textual data).
The (column) vectors of Table~1 are subdivided into five groups:
\begin{align*}
&G_1 = \range{T_1}{\rangeall}{1},
&G_2 = \range{T_1}{\rangeall}{2},\\
&G_3 = \range{T_1}{\rangeall}{\rangeto{3}{8}},
&G_4 = \range{T_1}{\rangeall}{9},\\
&G_5 = \range{T_1}{\rangeall}{\rangeto{10}{11}}
\end{align*}.
In order to sum the results of a salesperson across quarters we can consider for example the subgroup $\range{T_1}{\rangeall}{\rangeto{3}{6}} \subset G_3$

\subsection{Constraints}
A \textit{Spreadsheet constraint} is a triple \textit{(\CName, \CSignature, \CFunction)}.
Let us elaborate on each of them. 
\begin{itemize}
\item
\textit{\CName} is the textual name of the constraint together with the list of its variables $v_1,\dots,v_n$.
\item
  \textit{\CSignature} is a set of constraints on the properties of the group assignments, corresponding to the variables $v_1,\dots,v_n$ in \CName.
  For example, the signature can restrict the types of the groups, e.g., requiring them to be integers or constrain their sizes, e.g. the length of vectors in the arguments must be equal.
  The constraints act on porperties or group meta-information, not on the actual group content. 
\item \textit{\CFunction} is a constraint specifying that the data in the subgroups satisfies the function.
  \end{itemize}

\paragraph{Example}
\sergey{need to use this below:}
  For example, a spreadsheet constraint \textit{rank} has \CName \textit{$v_r$ = RANK($v_x$)}, where $v_x$ and $v_r$ are its variables; its \CSignature is: groups assigned to $v_x$ must be numeric, groups assigned to $v_y$ must be integer and the length of vectors in $v_x$ is the same as in $v_y$; its \CFunction is the following constraint: the mapping $\{ v_x \mapsto G_x', v_y \mapsto G_y' \}$ is a solution iff $G_x' \subset G_x, G_y' \subset G_y$ ($G_x \in \groups, G_y \in \groups$) and each value in $G_y'$ is the rank of the corresponding value in $G_x'$ (possibly with ties).

@@

While the traditional CSP problem is given a set of cells and a set of constraints,
and the task is to find an assignment, the {\bf inverse CSP} or the {\bf Tabular Constraint Learning Problem} can be defined as follows.\\
\\
{\bf Given }
\begin{itemize}
\item
a set of instantiated tables (so all cells have values) ${\cal T}$;
\item
a set of spreadsheet constraints ${\cal C}$;
\item
a set of groups ${\cal G}$ for the tables ${\cal T}$;
\end{itemize}
\noindent
\samuel{This section is incorrect, yet, we find assignments over subgroups, associated with a spreadsheet constraint}
{\bf Find}  the set $C\subset {\cal C}$ that contains all constraints $c(G_1, ... , G_N)$ that 1) are satisfied  in ${\cal T}$, 2)
for which
all $G_i \in {\cal G}$ and  3)  $c(G_1, ... , G_N)$ satisfies the signature of the constraint $c$.

>>>>

\paragraph{Example}
Consider Table~1 in the Figure~\ref{fig:main_example}, its rows are not type consistent (i.e. they contain both numeric and textual data).
The (column) vectors of Table~1 are subdivided into five groups:
\begin{align*}
&G_1 = \range{T_1}{\rangeall}{1},
&G_2 = \range{T_1}{\rangeall}{2},\\
&G_3 = \range{T_1}{\rangeall}{\rangeto{3}{8}},
&G_4 = \range{T_1}{\rangeall}{9},\\
&G_5 = \range{T_1}{\rangeall}{\rangeto{10}{11}}.
\end{align*}
In order to sum the results of a salesperson across quarters we can consider for example the subgroup $\range{T_1}{\rangeall}{\rangeto{3}{6}} \subset G_3$

\subsection{Constraints}
\sergey{write correspondence with ILP terminology}
A \textit{Spreadsheet constraint} is a triple \textit{(\CName, \CSignature, \CFunction)}.
Let us elaborate on each of them. 
\begin{itemize}
\item
\textit{\CName} is the textual name of the constraint together with the list of its variables $v_1,\dots,v_n$.
\item
  \textit{\CSignature} is a set of constraints on the properties of the group assignments, corresponding to the variables $v_1,\dots,v_n$ in \CName.
  For example, the signature can restrict the types of the groups, e.g., requiring them to be integers or constrain their sizes, e.g. the length of vectors in the arguments must be equal.
  The constraints act on porperties or group meta-information, not on the actual group content. 
\item \textit{\CFunction} is a constraint specifying that the data in the subgroups satisfies the function.
  \end{itemize}

\paragraph{Example}
\sergey{need to use this below:}
  For example, a spreadsheet constraint \textit{rank} has \CName \textit{$v_r$ = RANK($v_x$)}, where $v_x$ and $v_r$ are its variables; its \CSignature is: groups assigned to $v_x$ must be numeric, groups assigned to $v_y$ must be integer and the length of vectors in $v_x$ is the same as in $v_y$; its \CFunction is the following constraint: the mapping $\{ v_x \mapsto G_x', v_y \mapsto G_y' \}$ is a solution iff $G_x' \subseteq G_x, G_y' \subseteq G_y$ ($G_x \in \groups, G_y \in \groups$) and each value in $G_y'$ is the rank of the corresponding value in $G_x'$ (possibly with ties).

@@

While the traditional CSP problem is given a set of cells and a set of constraints,
and the task is to find an assignment, the {\bf inverse CSP} or the {\bf Tabular Constraint Learning Problem} can be defined as follows.\\
\\
{\bf Given }
\begin{itemize}
\item
a set of instantiated tables (so all cells have values) ${\cal T}$;
\item
a set of spreadsheet constraints ${\cal C}$;
\item
a set of groups ${\cal G}$ for the tables ${\cal T}$;
\end{itemize}
\noindent
\samuel{This section is incorrect, yet, we find assignments over subgroups, associated with a spreadsheet constraint}
{\bf Find}  the set $C\subseteq {\cal C}$ that contains all constraints $c(G_1, ... , G_N)$ that 1) are satisfied  in ${\cal T}$, 2)
for which
all $G_i \in {\cal G}$ and  3)  $c(G_1, ... , G_N)$ satisfies the signature of the constraint $c$.
